\textls[-0]{\thetitle}

### 2023-03-03 related-work.tex
add para on ML modules

\noindentparagraph{Solutions to the expression problem} \!abound.
% \EDJ{I have been meaning to ask but is this ``abound'' you intentionally put outside of the boldfont?}\YZreply{Yes}
Almost all involve some form of either explicit or implicit parameterization
as extensibility hooks.
Our approach is the first that applies family polymorphism~\cite{ernst2001family},
an idea from the context of OO languages,
to the context of mechanized proofs.
%Families in \Lang are second-class, in that they are not considered
%terms by themselves.
%Families as modeled in \TT (namely linkages) are first-class and thus more flexible.\EDJ{A more unified way is to consider Coq's Family (our surface syntax) second class corresponds to Inheritance Judgement/Linkage Transformer (secondclass in type theory). Linkage transformer is the helper function to construct first class linkage easily. Even non-derived (surface syntax) family can be considered in this way because they are just inheritance on empty family.}
%The distinction corresponds to class-based vs.\ object-base family
%polymorphism as summarized before~\cite{cdnw07-tribe}.

\citet{bac2006} address the expression problem for a core subset of Standard~ML
by combining explicitly coded open recursion with a mechanism that
allows pattern-matching cases to be defined separately and combined
later.
Our \lsti{FRecursion} and \lsti{FInduction} commands achieve a similar
functionality, with families making open recursion implicit and
bestowing organizational power.

>>>>

\noindentparagraph{Solutions to the expression problem} \!abound.
% \EDJ{I have been meaning to ask but is this ``abound'' you intentionally put outside of the boldfont?}\YZreply{Yes}
Almost all involve some form of either explicit or implicit parameterization
as extensibility hooks.
Our approach is the first that applies family polymorphism~\cite{ernst2001family},
an idea from OO research,
to the context of mechanized proofs.
%Families in \Lang are second-class, in that they are not considered
%terms by themselves.
%Families as modeled in \TT (namely linkages) are first-class and thus more flexible.\EDJ{A more unified way is to consider Coq's Family (our surface syntax) second class corresponds to Inheritance Judgement/Linkage Transformer (secondclass in type theory). Linkage transformer is the helper function to construct first class linkage easily. Even non-derived (surface syntax) family can be considered in this way because they are just inheritance on empty family.}
%The distinction corresponds to class-based vs.\ object-base family
%polymorphism as summarized before~\cite{cdnw07-tribe}.

\citet{bac2006} address the expression problem for a core subset of Standard~ML
by combining explicitly coded open recursion with a design that
allows pattern-matching cases to be defined separately and combined
later.
Our \lsti{FRecursion} and \lsti{FInduction} commands achieve a similar
functionality, with families making open recursion implicit and
bestowing organizational power.

\noindentparagraph{ML-style modules}\!\!, like families, are a modularity mechanism,
but with a focus on abstraction rather than extensibility.
Both \TT and the module system of \citet{stohar2000} use singletons to model and
control the propagation of definitions.
\mbox{MixML} \cite{rosdre2013} integrates mixins into ML and handles the
idiosyncrasies of ML modules,
while our work supports mixins in the presence of extensible inductive types.
